---
title: "NewProjRBSI"
author: "Sevastian Sanchez"
date: "2023-08-17"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(stargazer)
library(car)
```

# H1: Research Question: Is academic freedom affected by regime transition? 
# What is the independent variable(x)? Regime transition 
# What is the dependent variable(y)? Academic Freedom 
# What is the unit of analysis? Countries experiencing transition 

# Loading, Extracting & Cleaning Data 
```{r}
#loading & extracting from vdem dataset
setwd("~/Desktop/RBSI/RBSI RESEARCH DATA/Democracy Measures")
vdem.all <-read.csv("V-Dem-CY-Full+Others-v13.csv")
vdem.all <- select(vdem.all, "country_name", "country_text_id", "year", "v2x_accountability", "v2x_libdem", "v2xca_academ", "e_gdppc", "e_wb_pop")

#loading & extracting from ert dataset
ert<-read.csv("ert.csv")
ert <- select(ert, "country_name", "country_text_id", "year", "v2x_regime", "row_regch_event", "reg_type", "reg_trans", "dem_ep", "dem_ep_start_year", "dem_ep_end_year", "aut_ep", "aut_ep_start_year", "aut_ep_end_year")

#Merging & rearranging df dataset
df<-merge(ert, vdem.all, by = c("year", "country_name", "country_text_id"))
df<- select(df, "country_name", "country_text_id", "year", "v2x_libdem", "v2xca_academ", "reg_type", "v2x_regime", "reg_trans", "dem_ep", "dem_ep_start_year", "dem_ep_end_year", "aut_ep", "aut_ep_start_year", "aut_ep_end_year", "e_gdppc", "e_wb_pop")
```

# Background info: 
```{r}
#Distribution of all countries that experienced democratization from 1900-2021
hist(df$year[df$reg_trans==1])
#Distribution of all countries that experienced democratic backsliding from 1900-2021
hist(df$year[df$reg_trans==-1])
#Distribution of all countries that have not experienced change  1900-2021
hist(df$year[df$reg_trans==0])

#frequency/proportion table: instances of backsliding, stability, democratization from 1900-2021
table(df$reg_trans) # frequency
prop.table(table(df$reg_trans)) # proportions 
```

```{r}
# The distribution of academic freedom for countries that have undergone democratic backsliding 
hist(df$v2xca_academ[df$reg_trans==-1], breaks = 10)
# The distribution of academic freedom for countries that have not experienced change 
hist(df$v2xca_academ[df$reg_trans==0], breaks = 10)
# The distribution of academic freedom for countries that have experienced democratization
hist(df$v2xca_academ[df$reg_trans==1], breaks = 10)
```

```{r}
#average academic freedom at the start year of regime backsliding  
df_backslide <- subset(df, reg_trans==-1)
mean(df_backslide$v2xca_academ)
```

```{r}
#All countries and their respective periods of regime transition (backsliding or democratizing)
df_deming <- subset(df, dem_ep==1)
df_auting <- subset(df, aut_ep==1)
```

#Evolution Cuban Academic Freedom (during backsliding) - [Connected Linegraph]
ggplot(df_auting, aes(x=year, y=v2xca_academ)) +
  geom_line(color="blue", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Academic Freedom - Regime backsliding")

#CUBA
```{r}
#CUBA DataFrame (during backsliding)
df_cub_aut <- subset(df_auting, country_text_id=="CUB")
# Cuba - Academic Freedom over time 
scatterplot(v2xca_academ ~ year, data=df_cub_aut)
# Cuba - regime change over time 
scatterplot(v2x_libdem ~ year, data=df_cub_aut)
# Cuba - Regime change & Academic Freedom 
scatterplot(v2xca_academ ~ v2x_libdem, data=df_cub_aut)
```


```{r}
#Evolution Cuban Academic Freedom (during backsliding) -  [Connected Linegraph]
ggplot(df_cub_aut, aes(x=year, y=v2xca_academ)) +
  geom_line(color="blue", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Cuban Academic Freedom - Regime transition")

#Evolution Cuban Academic Freedom & Democracy (during backsliding) [Connected Linegraph]
plot(df_cub_aut$v2xca_academ, type="o", main ="testing", xlab="year", ylab="Academic Freedom", col="blue", ylim=c(0, 1.0))
lines(df_cub_aut$v2x_libdem, ylab="Liberal Democracy", col="black")

#CUBA DataFrame (all time)
df_cub <- subset(df, country_text_id=="CUB")
# Cuba - Academic Freedom over time 
scatterplot(v2xca_academ ~ year, data=df_cub)
# Cuba - regime change over time 
scatterplot(v2x_libdem ~ year, data=df_cub)
# Cuba - Regime change & Academic Freedom 
scatterplot(v2xca_academ ~ v2x_libdem, data=df_cub)

#Evolution Cuban Academic Freedom - 1900-2021 (all time) [Connected Linegraph]
ggplot(df_cub, aes(x=year, y=v2xca_academ)) +
  geom_line(color="blue", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Cuban Academic Freedom")

#Evolution Cuban Academic Freedom & Democracy - 1900-2021 (all time)[Connected Linegraph]
plot(df_cub$v2xca_academ, type="o", main ="testing", xlab="year", ylab="Academic Freedom", col="blue", ylim=c(0, 1.0))
lines(df_cub$v2x_libdem, ylab="Liberal Democracy", col="black")
```

#SPAIN
```{r}
# SPAIN DataFrame (during backsliding)
df_esp_aut <- subset(df_auting, country_text_id=="ESP")
# Mexico - Academic Freedom over time 
scatterplot(v2xca_academ ~ year, data=df_esp_aut)
# Mexico - regime change over time 
scatterplot(v2x_libdem ~ year, data=df_esp_aut)
# Mexico - Regime change & Academic Freedom 
scatterplot(v2x_libdem ~ v2xca_academ, data=df_esp_aut)

#Evolution Spanish Academic Freedom (during backsliding) [Connected Linegraph]
ggplot(df_esp_aut, aes(x=year, y=v2xca_academ)) +
  geom_line(color="red", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Spanish Academic Freedom")

#Evolution Spanish Academic Freedom & Democracy (during backsliding) [Connected Linegraph]
plot(df_esp_aut$v2xca_academ, type="o", main ="Evolution Spanish Academic Freedom & Democracy during regime change", xlab="year", ylab="Academic Freedom", col="red", ylim=c(0, 1.0))
lines(df_esp_aut$v2x_libdem, ylab="Liberal Democracy", col="black")

# SPAIN DataFrame (all time)
df_esp <- subset(df, country_text_id=="ESP")
# Mexico - Academic Freedom over time 
scatterplot(v2xca_academ ~ year, data=df_esp)
# Mexico - regime change over time 
scatterplot(v2x_libdem ~ year, data=df_esp)
# Mexico - Regime change & Academic Freedom 
scatterplot(v2x_libdem ~ v2xca_academ, data=df_esp)

#Evolution Spanish Academic Freedom - 1900-2021 (all time) [Connected Linegraph]
ggplot(df_esp, aes(x=year, y=v2xca_academ)) +
  geom_line(color="red", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Spanish Academic Freedom")

#Evolution Spanish Academic Freedom & Democracy - 1900-2021 (all time) [Connected Linegraph]
plot(df_esp$v2xca_academ, type="o", main ="testing", xlab="year", ylab="Academic Freedom", col="red", ylim=c(0, 1.0))
lines(df_esp$v2x_libdem, ylab="Liberal Democracy", col="black")
```

#MEXICO
```{r}
# MEXICO DataFrame
df_mex <- subset(df, country_text_id=="MEX")
# Mexico - Academic Freedom over time 
scatterplot(v2xca_academ ~ year, data=df_mex)
# Mexico - regime change over time 
scatterplot(v2x_libdem ~ year, data=df_mex)
# Mexico - Regime change & Academic Freedom 
scatterplot(v2x_libdem ~ v2xca_academ, data=df_mex)

#Evolution Mexican Academic Freedom - 1900-2021 [Connected Linegraph]
ggplot(df_mex, aes(x=year, y=v2xca_academ)) +
  geom_line(color="green", size=1, alpha=1, linetype=1) +
  geom_point(shape=21, color="black", fill="black", size=.5)
ggtitle("Evolution Mexican Academic Freedom")

#Evolution Mexican Academic Freedom & Democracy - 1900-2021 [Connected Linegraph]
plot(df_mex$v2xca_academ, type="o", main ="testing", xlab="year", ylab="Academic Freedom", col="green", ylim=c(0, 1.0))
lines(df_mex$v2x_libdem, ylab="Liberal Democracy", col="black")
```

# H2: Research Question: Is innovation affected by regime transition? 
# What is the independent variable(x)? Regime transition 
# What is the dependent variable(y)? Scientific Innovation
# What is the unit of analysis? Countries experiencing transition 
## Countries of Interest: USSR/Russia, Chile, Venezuela, Cuba, Spain, Germany, Singapore 

#Including Innovation in Dataframe 
patentapps.res <- read.csv("patentapps_res.csv")
hist(df_auting$v2xca_academ[df_auting$year>1980], breaks = 10)

hist(patentapps.res$Country.Code=="ARG", breaks = 10)

patentapps.res1 <- rename(patentapps.res, country_text_id = Country.Code)
S_T_Jour_Art<- read.csv("SciTechJourArtc.csv")
S_T_Jour_Art1 <- rename(S_T_Jour_Art, country_text_id = Country.Code)
df_1 <- merge(df, patentapps.res2, by = "country_text_id")
df_innov <- merge(df_1, S_T_Jour_Art2, by = "country_text_id")
View(df_innov)

df<- subset(ert, reg_trans==1 | reg_trans==-1)
