---
title: "RBSI RP-H1"
author: "Sevastian Sanchez"
date: "2023-06-23"
output: pdf_document
---

```{r setup, include=FALSE}

## Set working directory
rm(list=ls())
# Write your working directory
setwd("~/Desktop/RBSI - R Files/RESEARCH/DATA")

knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(dplyr)
library(tidyr)
library(stargazer)
library(readr)
library(ggplot2)
library(stringr)

```

## R Markdown

```{r load data}
# V_dem & innovation -- standardized 
finaldf <- read.csv("finaldf.csv")

# Standarize the varibles into normal distributions
finaldf <- finaldf %>% mutate(nonres_pat_z = scale(nonres_pat),
                              res_pat_z = scale(res_pat),
                              journal_art_z = scale(journal_art),
                              libdem_diff = v2x_libdem-libdem2017)
#remove irrelavent columns
finaldf <- finaldf[-c(14, 17)]

```

H1: Academic freedom correlation to innovation, Regime type-constant

```{r H1a,b}

# AFI(x) - patent apps-non-residents(y) (Innov) correlation

AFI_Innov1 <- lm(finaldf$res_pat_z ~ finaldf$v2xca_academ + finaldf$v2x_regime_amb + finaldf$e_gdppc + finaldf$e_wb_pop)

# AFI(x) - patent apps-residents(y) (Innov) correlation
AFI_Innov2 <- lm(finaldf$nonres_pat_z ~ finaldf$v2xca_academ + finaldf$v2x_regime_amb + finaldf$e_gdppc + finaldf$e_wb_pop)

# AFI(x) - journal_art(y) (Innov) correlation

AFI_Innov3 <- lm(finaldf$journal_art_z ~ finaldf$v2xca_academ + finaldf$v2x_regime_amb + finaldf$e_gdppc + finaldf$e_wb_pop)

stargazer(AFI_Innov1, AFI_Innov2, AFI_Innov3, title = "Academic Freedom Effects on Different Innovation Variables, holding regime type constant", type ="text")

```

```{r SUBSETTING}
#ACADEMIC FREEDOM EFFECT ON INNOVATION WITHIN AUTOCRACIES 

finaldf.auto <- subset(finaldf, v2xca_academ <= 5)

AFI_Innov1.auto <- lm(res_pat_z ~ v2xca_academ + e_gdppc + e_wb_pop, data= finaldf.auto)
AFI_Innov2.auto <- lm(nonres_pat_z ~ v2xca_academ +  e_gdppc + e_wb_pop, data= finaldf.auto)
AFI_Innov3.auto <- lm(journal_art_z ~ v2xca_academ + e_gdppc + e_wb_pop, data= finaldf.auto)

stargazer(AFI_Innov1.auto, AFI_Innov2.auto, AFI_Innov3.auto, title = "Academic freedom effects on different innovation variables in autocratic regimes, holding regime type constant", type = "text")
```


```{r load data}
# V_dem & innovation -- standardized 
finaldf <- read.csv("finaldf.csv")

# Standarize the varibles into normal distributions
finaldf <- finaldf %>% mutate(nonres_pat_z = scale(nonres_pat),
                              res_pat_z = scale(res_pat),
                              journal_art_z = scale(journal_art),
                              libdem_diff = v2x_libdem-libdem2017)
#remove irrelavent columns
finaldf <- finaldf[-c(14, 17)]
```

H2: Regime type correlation with innovation 
```{r H2}
# H2a
# LDem(x) - patent apps-residents(y) (Innov) correlation

LDem_Innov1 <- lm(finaldf$res_pat_z ~ finaldf$v2x_libdem + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)

# LDem_Innov1.1 [v2x_regime_amb]
LDem_Innov1.1 <- lm(finaldf$res_pat_z ~ finaldf$v2x_regime_amb + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)
```
H2: Regime type correlation with innovation 
```{r}
# H2b
# LDem(x) - patent apps-nonresidents(y) (Innov) correlation

LDem_Innov2 <- lm(finaldf$nonres_pat_z ~ finaldf$v2x_libdem + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)

#LDem_Innov2.1 [v2x_regime_amb]
LDem_Innov2.1 <- lm(finaldf$nonres_pat_z ~ finaldf$v2x_regime_amb + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)
```
H2: Regime type correlation with innovation 
```{r}
# H2c
# LDem(x) - sciarticles(y) (Innov) correlation
LDem_Innov3 <- lm(finaldf$journal_art_z ~ finaldf$v2x_libdem + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)

#LDem_Innov3.1 [v2x_regime_amb]
LDem_Innov3.1 <- lm(finaldf$journal_art_z ~ finaldf$v2x_regime_amb + finaldf$v2xca_academ + finaldf$e_gdppc + finaldf$e_wb_pop)

stargazer(LDem_Innov1, LDem_Innov2, LDem_Innov3, title = "Effect of Democracy Score (Liberal Democracy Score) on Different Innovation Measures, holding academic freedom constant", type ="text")

stargazer(LDem_Innov1.1, LDem_Innov2.1, LDem_Innov3.1, title = "Effect of Regime Type (Regimes of the World - Ambiguous) on Different Innovation Measures, holding academic freedom constant", type ="text")
summary(LDem_Innov3)
```
```{r insert and clean_Data}
# VARS = GDP, Population, AFI, Liberal Democracy Index, RoW(ambiguous) Index, country_name, country_id, country_code, year, y2015-2022, y2015, y2018

vdem_recent <- read.csv("vdem_recent.csv")
names(vdem_recent)[names(vdem_recent) == "y2015_2021"] <- "y2015_2022"

## Identify the variables you need (independent, dependent, and controls)...

# Regime Type (x) = Independent var (V-dem Democracy indices)
# Academic Freedom (y) = Dependent var (Academic Freedom Index)

# Academic Freedom (x) = Independent var
# Scientific Innovation (y) = Dependent var

```

H3: FINDING OVERALL VARIATION: RECENT DATA - 1980-2021
```{r across regimes}

##### Using 'v2x_libdem'-- across regimes #####
m1.all <- lm(v2xca_academ ~ v2x_libdem + e_wb_pop + e_gdppc, data = vdem_recent)

#scatter plot
m1.all.plot <- plot(vdem_recent$v2xca_academ ~ vdem_recent$v2x_libdem + vdem_recent$e_wb_pop + vdem_recent$e_gdppc,
                    main = "regime type and academic freedom relationship", 
                    xlab = "regime type - libdem", 
                    ylab = "academic freedom")

#correlation - M1
cor.test(vdem_recent$v2xca_academ, vdem_recent$v2x_libdem + vdem_recent$e_wb_pop + vdem_recent$e_gdppc)
```

H3: SUBSETTING: FINDING VARIATION AMONG AUTOCRACIES, 1980-2021
```{r regression, subsetting by regime type}
#subset for autocracies - scatter plot
vdem_rec_auto <- subset(vdem_recent, v2x_libdem < 0.51)
```
H3: FINDING VARIATION AMONG AUTOCRACIES, 1980-2021
```{r regression, autocracies & academic freedom, data = vdem_rec_auto1}

##### ROUND 2: Using 'v2x_libdem' #####
m1.auto <- lm(v2xca_academ ~ v2x_libdem + e_wb_pop + e_gdppc, data = vdem_rec_auto)

#scatter plot 
m1.auto.plot <- plot(v2xca_academ ~ v2x_libdem + e_wb_pop + e_gdppc, data = vdem_rec_auto,  
     main = "autocratic regime and academic freedom relationship", 
     xlab="regime type - libdem", 
     ylab="academic freedom") 

#correlation - M1
cor.test(vdem_rec_auto$v2xca_academ, vdem_rec_auto$v2x_libdem + vdem_rec_auto$e_wb_pop + vdem_rec_auto$e_gdppc)
```

H3: SUBSETTING: FINDING VARIATION AMONG DEMOCRACIES, 1980-2021
```{r}
#subset for democracies - scatter plot
vdem_rec_dem <- subset(vdem_recent, v2x_libdem > 0.49)
```

H3: FINDING VARIATION AMONG DEMOCRACIES, 1980-2021
```{r regression, democracies & academic freedom, data = vdem_rec_dem}

m1.dem <- lm(v2xca_academ ~ v2x_libdem + e_wb_pop + e_gdppc, data = vdem_rec_dem)

# scatterplot
m1.dem.plot <- plot(v2xca_academ ~ v2x_libdem + e_wb_pop + e_gdppc, data = vdem_rec_dem,
     main = "democracies and academic freedom relationship", 
     xlab="regime type - libdem(>0.5)", 
     ylab="academic freedom")

stargazer(m1.all, m1.dem, title="All, Autocratic, and Democratic Regimes", type ="text")
```
